---
title: "Wrangle and analyze job descriptions from indeed.com"
author: "Andrew Winter"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Why process text in R?
R has a huge selection of inuitive, charismatic packages. It has immediate practical use for data analysis, and it pairs well for general-purpose applications. 

By organizing job postings into a tidy format, we can effectively interpret text as data, and use that data to try to improve decision-making. In this case, analyzing word choice and frequency might inform the kind of language folks like to use when evaluating candidates' experience.


```{r packages, message=FALSE}
# load required packages
library(tidyverse)
library(rvest)
library(tidytext)
```



```{r}
base_url <- "https://www.indeed.com"
read_html(base_url)

# url for searching "R, data analyst" in Los Angeles
search_url <- paste0(base_url, "/jobs?q=R%2C+Data+Analyst&l=Los+Angeles")

test_session1 <- html_session(search_url)
test_session1

test_form1 <- html_form(test_session1)[[1]]
# html_form gives back two forms, a GET and a POST

test_form2 <- submit_form(test_session1, test_form1)

test_nodeset <- test_form2 %>%
  html_nodes("a.jobtitle")

test_df <- tibble(
  role_title = test_nodeset %>%
    html_text("title") %>%
    str_replace_all("\n", ""),
  role_url = test_nodeset %>%
    html_attr("href") %>%
    paste0(base_url, .)
)

test_df$role_url[1] %>%
  html_session() %>%

```


I can copy and paste this link in my browser, and Inspect Element to manually look at the HTML. **Will add pictures here as needed**



```{r}
search_nodeset <- search_url %>%
  read_html() %>%
  html_nodes("a.jobtitle")

# the argument for html_nodes() is a CSS selector
# extract hyperlink elements whose class is "jobtitle"
# the Chrome extension SelectorGadget is very useful for finding CSS selectors

search_nodeset

search_df <- tibble(
  role_title = search_nodeset %>%
    html_text("title") %>%
    str_replace_all("\n", ""),
  role_url = search_nodeset %>%
    html_attr("href") %>%
    paste0(base_url, .)
)

search_df
```


Just a little research is required for finding the CSS selectors that correspond with the info I want.


```{r}
sample_html <- read_html(search_df$role_url[1])

sample_html %>%
  html_nodes(".jobsearch-JobInfoHeader-title") %>%
  html_text()
```


Rather than copying and pasting this code, it makes sense to write a function for extracting text based on a CSS selector. While I'm at it, I'll make sure it either extracts the text safely or returns NA.


```{r}
safe_extract_text <- function(html_class, str_to_css){
  if ("xml_node" %in% class(html_class) |
      "xml_document" %in% class(html_class)) {
    html_class %>%
      html_nodes(str_to_css) %>%
      html_text()  
  } else {
    NA
  }
}

sample_html %>%
  safe_extract_text(".jobsearch-DesktopStickyContainer-companyrating div")

sample_html %>%
  safe_extract_text(".jobsearch-jobDescriptionText")
```


This is better, but I'm still calling the same function, multiple times in a row. I'll write a function that summarizes this info.

